 

### 2023-04-13 markdown/methods.Rmd
thesis: flowchart in methods started not knitting correctly --> fix to do

---
title: ''
output: pdf_document
---

# Materials and Methods

@@

## Data

#### Cell Isolation

#### Lysis

#### Digestion

#### Ionization

#### Coupled mass-spectrometry (MS/MS)

#### Labeling techniques

@@

##### Isobaric labeling

###### Tandem mass tag (TMT)

@@

>>>>

---
title: ''
output: pdf_document
---
# Materials and Methods

@@

### Cell Isolation

### Lysis

### Digestion

### Labeling techniques

@@

#### Isobaric labeling

##### Tandem mass tag (TMT)

@@

#### Mass Spectrometry

##### Ionization

##### MS.1

##### Coupled mass-spectrometry (MS/MS) & MS.2

## Data
```{r Dataflow,  echo=FALSE}
library(DiagrammeR)
library(webshot)

DiagrammeR::grViz("digraph {
	graph [layout  =  dot,
	       rankdir  = TB]

node [shape = rectangle]
rawData [label = 'msData.raw']
node [shape = oval]
MQ [label = 'MaxQuant']
node [shape = invhouse]
MQ_fd [label = 'feature detection']
node [shape = cylinder]
MQ_ds [label = 'Database search']
node [shape = invhouse]
MQ_fdr [label = 'FDR calculation']
MQ_quant [label = 'Protein Quantification']
node [shape = rectangle]
MQoutput [label = 'evidence.txt']
sampleAnnotate [label = 'sample_annotation.txt']
node [shape = oval]
ProteomicsWorkbench [label = 'Proteomics Workbench']

rawData -> MQ -> MQ_fd -> MQ_ds -> MQ_fdr -> MQ_quant -> MQoutput -> ProteomicsWorkbench
sampleAnnotate -> ProteomicsWorkbench
}",
height = 500)
```
